How to \emph{not} write Virtual Machines for Dynamic Languages

### 2007-05-27 talk/dyla2007/dyla.tex
change to the old title but italicize the "not". is -> was in the footnote.

\title{PyPy: raising the level for Dynamic Language implementations}

@@

Dynamic languages are traditionally implemented by writing a virtual machine for
them, centered around an interpreter and/or a built-in compiler and providing
the object model and memory management. When a language becomes more successful,
the limitations of such an implementation lead to the emergence of alternative
implementations that try to solve some of the problems. Another reason for new
implementations is the desire to have the language integrate well with existing,
well-tuned object-oriented virtual machine like Java's. In this paper, we
describe the mechanisms that lead to an abundance of implementations, and
explore some of the limitations of standard VMs.  We propose a different
complementary alternative to writing VMs by hand and dealing with low-level
details, validated by the PyPy project: flexibly generating virtual machines
from a single abstract language ``specification'', inserting features and
low-level details automatically -- including good just-in-time compilers tuned
to the dynamic language at hand.
\footnote{This research is partially supported by the EU funded
 project: IST 004779 PyPy (PyPy: Implementing Python in Python).} \\

>>>>

\title{How to \emph{not} write Virtual Machines for Dynamic Languages}

@@

Dynamic languages are traditionally implemented by writing a virtual machine for
them, centered around an interpreter and/or a built-in compiler and providing
the object model and memory management. When a language becomes more successful,
the limitations of such an implementation lead to the emergence of alternative
implementations that try to solve some of the problems. Another reason for new
implementations is the desire to have the language integrate well with existing,
well-tuned object-oriented virtual machine like Java's. In this paper, we
describe the mechanisms that lead to an abundance of implementations, and
explore some of the limitations of standard VMs.  We propose a different
complementary alternative to writing VMs by hand and dealing with low-level
details, validated by the PyPy project: flexibly generating virtual machines
from a single abstract language ``specification'', inserting features and
low-level details automatically -- including good just-in-time compilers tuned
to the dynamic language at hand.
\footnote{This research was partially supported by the EU funded
 project: IST 004779 PyPy (PyPy: Implementing Python in Python).} \\
